\huge A Usability Evaluation of Tor Launcher

### 2017-03-15 pets2017-paper/pets2017-paper.tex
wordsmith background (section 2) for formatting; time for really pretty pages

\section{Technical Background}
\label{sec:background}
This section discusses how to connect to Tor and what network components are involved.

@@

A connection to Tor involves many interacting components,
illustrated in Figure~\ref{fig:topology}.
It may involve a proxy and a bridge,
possibly in the presence of a censor.

The word ``proxy'' has a specific meaning in the context of a Tor connection.
Generally, a proxy is any computer or service that allows its users to make indirect network connections to other services. In this sense, any Tor relay and the Tor circuit can also be considered to be a proxy. However, in this paper, the word ``proxy'' refers to a SOCKS or HTTP proxy that bypasses local firewalls.

@@

Users can configure a bridge by choosing a transport (Figure~\ref{fig:old-bridge-combobox}), which selects the group of bridges that use that transport. If the built-in bridges do not work, users can obtain bridge configurations through out-of-band channels~\cite{bridgedb} that provide the necessary information. Configuring a proxy requires entering in the proxy protocol, IP address, port, and additional optional fields (Figure~\ref{fig:old-proxy}). The user must locate this information.

>>>>

\section{Technical Background}
\label{sec:background}
This section discusses the network components are involved in connecting to Tor and how users can connect to Tor in various ways. An understanding of the network components or the various connection options are not required to understand our work, but we refer to these terms and methods throughout the paper.

@@

A connection to Tor involves many interacting components,
illustrated in Figure~\ref{fig:topology}.
In the presence of a local firewall and censor, it may involve a proxy and a bridge.

The word ``proxy'' has a specific meaning in the context of a Tor connection.
Generally, a proxy is any computer or service that allows users to make indirect connections to other services. In this sense, any Tor relay and the Tor circuit can also be considered to be a proxy. However, in this paper, the word ``proxy'' refers to a SOCKS or HTTP proxy that bypasses local firewalls.

@@

Users can configure a bridge by choosing a transport, which selects the group of bridges that use that transport. For instance, choosing the ``obfs3'' option in Figure~\ref{fig:old-bridge-combobox} will select a group of bridges that peform the obfs3 transport protocol as okay to use, and the user will be assigned one of these bridges as their guard relay. If these built-in options do not work, users can obtain bridge configurations through out-of-band channels~\cite{bridgedb}. Configuring a proxy requires entering in the proxy protocol, IP address, port, and additional optional fields (Figure~\ref{fig:old-proxy}). The user must locate this information.
